### 2017-09-21 reports/thesis/book.tex
Produced VarBias2 graphs into thesis.

\chapter{Inference}
%\begin{equation*}
%i=1,2,3,\dotdotdot,n_{pixel}
%\end{equation*}
%\begin{equation*}
%j=1,2,3,\dotdotdot,n_{repeat}
%\end{equation*}
%\begin{equation*}
%x_i^{(j)} = \text{mean greyvalue of pixel }i\text{, }j\text{th repeat}
%\end{equation*}
%\begin{equation*}
%y_i^{(j)} = \text{variance greyvalue of pixel }i\text{, }j\text{th repeat}
%\end{equation*}
%\begin{equation*}
%\widehat{Y}^{(j)}(x) = \text{predicted variance greyvalue given }x
%\end{equation*}
%Trained $\widehat{Y}^{(j)}(x)$ using $(y_1^{(j)},x_1^{(j)}),(y_2^{(j)},x_2^{(j)}),(y_3^{(j)},x_3^{(j)}),\dotdotdot,(y_{n_{pixel}}^{(j)},x_{n_{pixel}}^{(j)})$.
%\begin{equation*}
%\widehat{\zeta}^{(j)}(x) = \text{predicted variance of the variance greyvalue given }x
%\end{equation*}
%
%Below are the training statistics, but can be generalised to test statistics:
%\begin{equation}
%\text{MSE}^{(j)} = \sum_{i=1}^{n_{pixel}} \left[\widehat{Y}^{(j)}(x_i^{(j)}) - y_i^{(j)}\right]^2
%\end{equation}
%\begin{equation}
%\text{MSSE}^{(j)} = \sum_{i=1}^{n_{pixel}} \left[\dfrac{\widehat{Y}^{(j)}(x_i^{(j)}) - y_i^{(j)}}{\sqrt{\widehat{\zeta}^{(j)}(x_i^{(j)})}}\right]^2
%\end{equation}
%\begin{equation}
%\text{VAR}^{(j)} = \sum_{i=1}^{n_{pixel}}
%\left[
%\widehat{Y}^{(j)}(x_i^{(j)}) - \expectation(\widehat{Y}(x_i^{(j)}))
%\right]^2
%\end{equation}
%\begin{equation}
%\text{BIAS2}^{(j)} = \sum_{i=1}^{n_{pixel}}
%\left[
%\expectation(\widehat{Y}(x_i^{(j)}))
%-
%y_i^{(j)}
%\right]^2
%\end{equation}
%where
%\begin{equation}
%\expectation(\widehat{Y}(x_i^{(j)})) \approx
%\frac{1}{n_{repeat}}\sum_{j=1}^{n_{repeat}}
%\widehat{Y}^{(j)}(x_i^{(j)})
%\end{equation}
%
%\clearpage
%\begin{equation}
%Y(x) = y(x) + \epsilon(x)
%\end{equation}
%where
%\begin{equation}
%\expectation[\epsilon(x)] = 0, \quad \variance[\epsilon(x)] = \sigma^2(x) \ .
%\end{equation}
%The statistics for a given $x$ are:
%\begin{equation}
%\text{MSE}(x) = \expectation\left[
%(Y(x)-\widehat{Y}(x))^2
%\right]
%\end{equation}
%\begin{equation}
%\text{VAR}(x) = \expectation\left[
%(\widehat{Y}(x) - \expectation(\widehat{Y}(x))^2
%\right]
%\end{equation}
%\begin{equation}
%\text{BIAS2}(x) = \expectation\left[
%(\expectation(\widehat{Y}(x) - y(x))^2
%\right]
%\end{equation}
%\begin{equation}
%\sigma^2(x) = \expectation\left[
%(
%Y(x) - \expectation(Y(x))
%)^2
%\right] \ .
%\end{equation}
%
%$y(x)$ is unknown so the bias squared can be calculated using
%\begin{equation}
%\text{BIAS2}(X) = \text{MSE}(X) - \text{VAR}(X) - \sigma^2(x)
%\end{equation}
%
%The expectations were estimated using bootstrapped samples of $Y(x)$ and $\widehat{Y}(x)$.
%
%\clearpage
%
%\begin{figure}
%\centering
%    \centerline{
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{../figures/training_MSSE.eps}
%    \end{subfigure}
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{../figures/test_MSSE.eps}
%    \end{subfigure}
%    }
%    \caption{Mean squared standardised error}
%\end{figure}
%
%\begin{figure}
%\centering
%    \centerline{
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{../figures/training_MSE.eps}
%    \end{subfigure}
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{../figures/test_MSE.eps}
%    \end{subfigure}
%    }
%    \caption{Mean squared error}
%\end{figure}
%
%\begin{figure}
%\centering
%    \centerline{
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{../figures/training_var.eps}
%    \end{subfigure}
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{../figures/test_var.eps}
%    \end{subfigure}
%    }
%    \caption{Estimation variance}
%\end{figure}
%
%\begin{figure}
%\centering
%    \centerline{
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{../figures/training_bias2.eps}
%    \end{subfigure}
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{../figures/test_bias2.eps}
%    \end{subfigure}
%    }
%    \caption{Bias squared}
%\end{figure}

>>>>

\chapter{Inference}
\begin{equation*}
i=1,2,3,\dotdotdot,n_{pixel}
\end{equation*}
\begin{equation*}
j=1,2,3,\dotdotdot,n_{fold}
\end{equation*}
\begin{equation*}
x = \text{mean greyvalue of a pixel}
\end{equation*}
\begin{equation*}
Y(x)= \text{variance greyvalue given }x
\end{equation*}
\begin{equation*}
\widehat{Y}(x) = \text{predicted variance greyvalue given }x
\end{equation*}

Let
\begin{equation}
Y(x) = f(x) + \epsilon(x)
\end{equation}
where
\begin{equation}
\expectation[\epsilon(x)] = 0, \quad \variance[\epsilon(x)] = \sigma^2(x)
\end{equation}
and
\begin{equation}
f(x) = \expectation\left[Y(x)\right] \ .
\end{equation}
The statistics for a given $x$ are:
\begin{equation}
\text{RSS}(x) = \expectation\left[
\left(\widehat{Y}(x) - Y(x)\right)^2
\right]
\end{equation}
\begin{equation}
\text{MSE}(x) = \expectation\left[
\left(\widehat{Y}(x)-f(x)\right)^2
\right]
\end{equation}
\begin{equation}
\text{BIAS}(x) = 
\expectation\left[\widehat{Y}(x)\right] - f(x)
\end{equation}
\begin{equation}
\text{VAR}(x) = \expectation\left[
\left(\widehat{Y}(x) - \expectation\left[\widehat{Y}(x)\right]\right)^2
\right]
\end{equation}
\begin{equation}
\sigma^2(x) = \expectation\left[
\left(Y(x) - f(x)\right)^2
\right] \ .
\end{equation}

Assuming $\expectation\left[\epsilon(x)\widehat{Y}(x)\right] = 0$, then
\begin{equation}
\text{MSE}(x) = \text{VAR}(x) + \text{BIAS}^2(x)
\end{equation}
and
\begin{equation}
\text{RSS}(x) = \text{MSE}(x) + \sigma^2(x)  .
\end{equation}

The images were spilt into a training set and a test set. The mean and variance of each pixel can be estimated for each set. This can be repeated multiple times by reassigning the training and test set. For the $j$th fold, $\widehat{Y}^{(j)}$ was trained using the training set.

For a given model and a given $x$, the following was observed for each fold after training using the training set
\begin{equation}
\widehat{Y}^{(1)}(x),\widehat{Y}^{(2)}(x),\widehat{Y}^{(3)}(x),\dotdotdot,\widehat{Y}^{(n_{fold})}(x)
\end{equation}
and for each fold in the test set
\begin{equation}
Y^{(1)}(x),Y^{(2)}(x),Y^{(3)}(x),\dotdotdot,Y^{(n_{fold})}(x)
\end{equation}
then the following can be estimated
\begin{equation}
f(x) \approx \frac{1}{n_{fold}}\sum_{j=1}^{n_{fold}}Y^{(j)}(x)
\end{equation}
\begin{equation}
\expectation\left[\widehat{Y}^{(j)}(x)\right] \approx \frac{1}{n_{fold}}\sum_{j=1}^{n_{fold}}\widehat{Y}^{(j)}(x)
\end{equation}
and:
\begin{equation}
\text{RSS}(x) \approx \frac{1}{n_{fold}}\sum_{j=1}^{n_{fold}} \left[
\left(\widehat{Y}^{(j)}(x) - Y^{(j)}(x)\right)^2
\right]
\end{equation}
\begin{equation}
\text{MSE}(x) \approx \frac{1}{n_{fold}}\sum_{j=1}^{n_{fold}} \left[
\left(\widehat{Y}^{(j)}(x)-f(x)\right)^2
\right]
\end{equation}
\begin{equation}
\text{BIAS}(x) \approx \frac{1}{n_{fold}}\sum_{j=1}^{n_{fold}} 
\left[\widehat{Y}^{(j)}(x)\right] - f(x)
\end{equation}
\begin{equation}
\text{VAR}(x) \approx \frac{1}{n_{fold}}\sum_{j=1}^{n_{fold}} \left[
\left(\widehat{Y}^{(j)}(x) - \expectation\left[\widehat{Y}^{(j)}(x)\right]\right)^2
\right]
\end{equation}
\begin{equation}
\sigma^2(x) \approx \frac{1}{n_{fold}}\sum_{j=1}^{n_{fold}} \left[
\left(Y^{(j)}(x) - f(x)\right)^2
\right] \ .
\end{equation}

\clearpage

\begin{figure}
\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/noiseidentity_order_1.eps}
        \caption{Identity, feature order 1}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/noisecanonical_order_-1.eps}
        \caption{Canonical, feature order -1}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/noisecanonical_order_-2.eps}
        \caption{Canonical, feature order -2}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/noiselog_order_-1.eps}
        \caption{Log, feature order -1}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/noisecanonical_order_-2.eps}
        \caption{Log, feature order -2}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/noise1000_NN.eps}
        \caption{1000-NN}
    \end{subfigure}
    }
\end{figure}

\begin{figure}
\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/mseidentity_order_1.eps}
        \caption{Identity, feature order 1}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/msecanonical_order_-1.eps}
        \caption{Canonical, feature order -1}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/msecanonical_order_-2.eps}
        \caption{Canonical, feature order -2}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/mselog_order_-1.eps}
        \caption{Log, feature order -1}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/msecanonical_order_-2.eps}
        \caption{Log, feature order -2}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/mse1000_NN.eps}
        \caption{1000-NN}
    \end{subfigure}
    }
\end{figure}

\begin{figure}
\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/biasidentity_order_1.eps}
        \caption{Identity, feature order 1}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/biascanonical_order_-1.eps}
        \caption{Canonical, feature order -1}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/biascanonical_order_-2.eps}
        \caption{Canonical, feature order -2}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/biaslog_order_-1.eps}
        \caption{Log, feature order -1}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/biascanonical_order_-2.eps}
        \caption{Log, feature order -2}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/bias1000_NN.eps}
        \caption{1000-NN}
    \end{subfigure}
    }
\end{figure}
